```{r}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/ggpubr")
```

Central_venous_LSECs"       
"Cholangiocytes"              "Non_inflammatory_Macrophage"
"alpha_beta_T_Cells"          "Inflammatory_Macrophage"    
"NK_like_Cells"               "gamma_delta_T_Cells_1"      
"Hepatocyte_5"                "Portal_endothelial_Cells"   
"gamma_delta_T_Cells_2"       "Periportal_LSECs"           
"Hepatocyte_6"                "Mature_B_Cells"             
"Hepatic_Stellate_Cells"      "Plasma_Cells"               
"Erythroid_Cells"             "Hepatocyte_2"               
"Hepatocyte_3"                "Hepatocyte_1"               
"Hepatocyte_4"

Central_venous_LSECs
```{r}
library("ggpubr")
p_sex_Central_venous_LSECs <- ggboxplot(merged_data, x = "SEX", y = "Central_venous_LSECs", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Central_venous_LSECs", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Central_venous_LSECs.png", plot = p_sex_Central_venous_LSECs)
```
```{r}
Central_venous_LSECs <- wilcox.test(Central_venous_LSECs ~ SEX, data = merged_data,
                   exact = FALSE)
Central_venous_LSECs
```

Cholangiocytes
```{r}
library("ggpubr")
p_sex_Cholangiocytes <- ggboxplot(merged_data, x = "SEX", y = "Cholangiocytes", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Cholangiocytes", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Cholangiocytes.png", plot = p_sex_Cholangiocytes)
```
```{r}
Cholangiocytes <- wilcox.test(Cholangiocytes ~ SEX, data = merged_data,
                   exact = FALSE)
Cholangiocytes
```

Non_inflammatory_Macrophage !!! 
```{r}
library("ggpubr")
p_sex_Non_inflammatory_Macrophage <- ggboxplot(merged_data, x = "SEX", y = "Non_inflammatory_Macrophage", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Non_inflammatory_Macrophage", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Non_inflammatory_Macrophage.png", plot = p_sex_Non_inflammatory_Macrophage)
```
```{r}
Non_inflammatory_Macrophage <- wilcox.test(Non_inflammatory_Macrophage ~ SEX, data = merged_data,
                   exact = FALSE)
Non_inflammatory_Macrophage
```

alpha_beta_T_Cells
```{r}
library("ggpubr")
p_sex_alpha_beta_T_Cells <- ggboxplot(merged_data, x = "SEX", y = "alpha_beta_T_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "alpha_beta_T_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_alpha_beta_T_Cells.png", plot = p_sex_alpha_beta_T_Cells)
```
```{r}
alpha_beta_T_Cells <- wilcox.test(alpha_beta_T_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
alpha_beta_T_Cells
```

Inflammatory_Macrophage
```{r}
library("ggpubr")
p_sex_Inflammatory_Macrophage <- ggboxplot(merged_data, x = "SEX", y = "Inflammatory_Macrophage", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Inflammatory_Macrophage", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Inflammatory_Macrophage.png", plot = p_sex_Inflammatory_Macrophage)
```
```{r}
Inflammatory_Macrophage <- wilcox.test(Inflammatory_Macrophage ~ SEX, data = merged_data,
                   exact = FALSE)
Inflammatory_Macrophage
```

NK_like_Cells
```{r}
library("ggpubr")
p_sex_NK_like_Cells <- ggboxplot(merged_data, x = "SEX", y = "NK_like_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "NK_like_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_NK_like_Cells.png", plot = p_sex_NK_like_Cells)
```
```{r}
NK_like_Cells <- wilcox.test(NK_like_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
NK_like_Cells
```

gamma_delta_T_Cells_1
```{r}
library("ggpubr")
p_sex_gamma_delta_T_Cells_1 <- ggboxplot(merged_data, x = "SEX", y = "gamma_delta_T_Cells_1", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "gamma_delta_T_Cells_1", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_gamma_delta_T_Cells_1.png", plot = p_sex_gamma_delta_T_Cells_1)
```
```{r}
gamma_delta_T_Cells_1 <- wilcox.test(gamma_delta_T_Cells_1 ~ SEX, data = merged_data,
                   exact = FALSE)
gamma_delta_T_Cells_1
```

Hepatocyte_5
```{r}
library("ggpubr")
p_sex_Hepatocyte_5 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_5", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_5", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_5.png", plot = p_sex_Hepatocyte_5)
```
```{r}
Hepatocyte_5 <- wilcox.test(Hepatocyte_5 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_5
```

Portal_endothelial_Cells`
```{r}
library("ggpubr")
p_sex_Portal_endothelial_Cells <- ggboxplot(merged_data, x = "SEX", y = "Portal_endothelial_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Portal_endothelial_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Portal_endothelial_Cells.png", plot = p_sex_Portal_endothelial_Cells)
```
```{r}
Portal_endothelial_Cells <- wilcox.test(Portal_endothelial_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
Portal_endothelial_Cells
```

gamma_delta_T_Cells_2
```{r}
library("ggpubr")
p_sex_gamma_delta_T_Cells_2 <- ggboxplot(merged_data, x = "SEX", y = "gamma_delta_T_Cells_2", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "gamma_delta_T_Cells_2", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_gamma_delta_T_Cells_2.png", plot = p_sex_gamma_delta_T_Cells_2)
```

```{r}
gamma_delta_T_Cells_2 <- wilcox.test(gamma_delta_T_Cells_2 ~ SEX, data = merged_data,
                   exact = FALSE)
gamma_delta_T_Cells_2
```

Periportal_LSECs
```{r}
library("ggpubr")
p_sex_Periportal_LSECs <- ggboxplot(merged_data, x = "SEX", y = "Periportal_LSECs", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Periportal_LSECs", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Periportal_LSECs.png", plot = p_sex_Periportal_LSECs)
```
```{r}
Periportal_LSECs <- wilcox.test(Periportal_LSECs ~ SEX, data = merged_data,
                   exact = FALSE)
Periportal_LSECs
```

Hepatocyte_6
```{r}
library("ggpubr")
p_sex_Hepatocyte_6 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_6", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_6", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_6.png", plot = p_sex_Hepatocyte_6)
```
```{r}
Hepatocyte_6 <- wilcox.test(Hepatocyte_6 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_6
```

Mature_B_Cells
```{r}
library("ggpubr")
p_sex_Mature_B_Cells <- ggboxplot(merged_data, x = "SEX", y = "Mature_B_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Mature_B_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Mature_B_Cells.png", plot = p_sex_Mature_B_Cells)
```
```{r}
Mature_B_Cells <- wilcox.test(Mature_B_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
Mature_B_Cells
```

Hepatic_Stellate_Cells
```{r}
library("ggpubr")
p_sex_Hepatic_Stellate_Cells <- ggboxplot(merged_data, x = "SEX", y = "Hepatic_Stellate_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatic_Stellate_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatic_Stellate_Cells.png", plot = p_sex_Hepatic_Stellate_Cells)
```
```{r}
Hepatic_Stellate_Cells <- wilcox.test(Hepatic_Stellate_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatic_Stellate_Cells
```

Plasma_Cells
```{r}
library("ggpubr")
p_sex_Plasma_Cells <- ggboxplot(merged_data, x = "SEX", y = "Plasma_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Plasma_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Plasma_Cells.png", plot = p_sex_Plasma_Cells)
```
```{r}
Plasma_Cells <- wilcox.test(Plasma_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
Plasma_Cells
```

Erythroid_Cells
```{r}
library("ggpubr")
p_sex_Erythroid_Cells <- ggboxplot(merged_data, x = "SEX", y = "Erythroid_Cells", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Erythroid_Cells", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Erythroid_Cells.png", plot = p_sex_Erythroid_Cells)
```
```{r}
Erythroid_Cells <- wilcox.test(Erythroid_Cells ~ SEX, data = merged_data,
                   exact = FALSE)
Erythroid_Cells
```

Hepatocyte_2
```{r}
library("ggpubr")
p_sex_Hepatocyte_2 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_2", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_2", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_2.png", plot = p_sex_Hepatocyte_2)
```
```{r}
Hepatocyte_2 <- wilcox.test(Hepatocyte_2 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_2
```

Hepatocyte_3
```{r}
library("ggpubr")
p_sex_Hepatocyte_3 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_2", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_3", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_3.png", plot = p_sex_Hepatocyte_3)
```
```{r}
Hepatocyte_3 <- wilcox.test(Hepatocyte_3 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_3
```

Hepatocyte_1
```{r}
library("ggpubr")
p_sex_Hepatocyte_1 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_1", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_1", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_1.png", plot = p_sex_Hepatocyte_1)
```
```{r}
Hepatocyte_1 <- wilcox.test(Hepatocyte_1 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_1
```

Hepatocyte_4
```{r}
library("ggpubr")
p_sex_Hepatocyte_4 <- ggboxplot(merged_data, x = "SEX", y = "Hepatocyte_4", 
          color = "SEX", palette = c("#00AFBB", "#E7B800"),
          main = "Cell type proportion according to sex", ylab = "Hepatocyte_4", xlab = "SEX")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_sex_Hepatocyte_4.png", plot = p_sex_Hepatocyte_4)
```
```{r}
Hepatocyte_4 <- wilcox.test(Hepatocyte_4 ~ SEX, data = merged_data,
                   exact = FALSE)
Hepatocyte_4
```

```{r}
pvalues <- c(Hepatocyte_4[["p.value"]], Hepatocyte_1[["p.value"]], Hepatocyte_3[["p.value"]], Hepatocyte_2[["p.value"]], Erythroid_Cells[["p.value"]], Plasma_Cells[["p.value"]], Hepatic_Stellate_Cells[["p.value"]], Mature_B_Cells[["p.value"]], Hepatocyte_6[["p.value"]], Periportal_LSECs[["p.value"]], gamma_delta_T_Cells_2[["p.value"]], Portal_endothelial_Cells[["p.value"]], Hepatocyte_5[["p.value"]], NK_like_Cells[["p.value"]], Inflammatory_Macrophage[["p.value"]], Non_inflammatory_Macrophage[["p.value"]], Cholangiocytes[["p.value"]], Central_venous_LSECs[["p.value"]])

p.adjust(pvalues,method="bonferroni")
```

```{r}
pvalues <- c(Hepatocyte_4[["p.value"]], Hepatocyte_1[["p.value"]], Hepatocyte_3[["p.value"]], Hepatocyte_2[["p.value"]], Erythroid_Cells[["p.value"]], Plasma_Cells[["p.value"]], Hepatic_Stellate_Cells[["p.value"]], Mature_B_Cells[["p.value"]], Hepatocyte_6[["p.value"]], Periportal_LSECs[["p.value"]], gamma_delta_T_Cells_2[["p.value"]], Portal_endothelial_Cells[["p.value"]], Hepatocyte_5[["p.value"]], NK_like_Cells[["p.value"]], Inflammatory_Macrophage[["p.value"]], Non_inflammatory_Macrophage[["p.value"]], Cholangiocytes[["p.value"]], Central_venous_LSECs[["p.value"]])

p.adjust(pvalues,method="BH")
```

both case no significant correlation ... 
sex too 
```{r}
p2_sex <- barplot(table(merged_data$SEX), 
        main = "Sex of our samples",
        xlab = "Sex: 1 = Male and 2 = Female",
        ylab = "Number of samples")
p2_sex

p2_sex <- recordPlot()
png("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p2_Liver_Sex_Nb.png", width = 6, height = 4, units = "in", res = 800)
replayPlot(p2_sex)
dev.off()
```

```{r}
# Compute the number of occurrences of "1" in the "sex" column
count_ones <- sum(merged_data$SEX == 1)

# Print the result
print(count_ones)
```

```{r}
# Compute the number of occurrences of "1" in the "sex" column
count_ones <- sum(merged_data$SEX == 2)

# Print the result
print(count_ones)
```




```{r}
library(viridis)
library(dplyr)
library(ggplot2)

# Generate a sequence of colors using the viridis palette
colors <- viridis(20)

p2S <- data_long %>%
  group_by(Cell_Type, SEX) %>%
  summarise(mf = mean(Fraction)) %>%
  ungroup() %>%
  ggplot(aes(x = factor(SEX), y = mf, fill = Cell_Type)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(title = "Cellular composition according to sex", x = "Sex: 1=Male and 2=Female", y = "Fraction of Cell Types") +
  theme_minimal() +
  theme(
    legend.key.width = unit(0.5, "cm"),  # Decrease the width of legend key
    legend.key.height = unit(0.5, "cm")  # Decrease the height of legend key
  )


p2S

p2S <- recordPlot()
png("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Sex_Liver_Cell_Comp.png", width = 6, height = 4, units = "in", res = 800)
replayPlot(p2S)
dev.off()
```



