---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

try echo=False
ggsave (filename, plot = plotname)

install.packages("tinytex")
tinytex::install_tinytex()


```{r}
library(biomaRt)
library(Seurat)
library(SeuratDisk)
library(tidyverse)
```



```{r}
setwd("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_")
```


```{r}
Liver_dec <- read.table("CIBERSORTx_Results_Liver.txt")
Liver_dec
```


```{r}
# Extract the first row of the data frame
first_row <- Liver_dec[1, ]

# Assign the values from the first row as column names
colnames(Liver_dec) <- first_row

# Remove the first row, as it's no longer needed as column names
Liver_dec <- Liver_dec[-1, ]

rownames(Liver_dec) <- NULL

# Display the resulting data frame
print(Liver_dec)
```


```{r}
names(Liver_dec)[names(Liver_dec) == "Mixture"] <- "SUBJID"
```



```{r}
colnames(Liver_dec)
Liver_dec
```



```{r}
age_sex <- read.csv("GTEx_Analysis_v8_Annotations_SubjectPhenotypes.txt", header = FALSE, sep = "\t")
age_sex
```

```{r}
# Extract the first row of the data frame
first_row <- age_sex[1, ]

# Assign the values from the first row as column names
colnames(age_sex) <- first_row

# Remove the first row, as it's no longer needed as column names
age_sex <- age_sex[-1, ]

rownames(age_sex) <- NULL

# Display the resulting data frame
print(age_sex)
```



```{r}
merged_data <- merge(Liver_dec, age_sex, by = "SUBJID", all.x = TRUE)
merged_data
```


```{r}
colnames(merged_data)
```



```{r}

# Function to calculate mid age from age range
calculate_mid_age <- function(age_range) {
  age_values <- as.numeric(strsplit(age_range, "-")[[1]])
  mid.age <- mean(age_values)
  return(mid.age)
}

# Apply the function to each row of merged_data and create a new column "mid_age"
merged_data$mid.age <- sapply(merged_data$AGE, calculate_mid_age)

# Print the dataframe to see the changes
print(merged_data)
```

```{r}
# Increase all numbers in the mid_age column by 0.5
merged_data$mid.age <- merged_data$mid.age + 0.5

# Print the dataframe to see the changes
print(merged_data)

```

```{r}
num_cols <- ncol(merged_data)

# Reorder the columns
new_order <- c(1:24, 28, 25:27, (29:num_cols)[(29:num_cols) <= num_cols])  # Define the new order of columns
merged_data <- merged_data[, new_order]  # Reorder the columns
merged_data <- merged_data[, -which(names(merged_data) == "mid.age.1")]
merged_data
```

```{r}
columns_to_convert <- 2:23

# Loop through each column and convert
for (col_index in columns_to_convert) {
   merged_data[[col_index]] <- round(as.numeric(as.character(merged_data[[col_index]])), digits = 3)
  # or if you want to round the values
  # merged_data[[col_index]] <- round(as.numeric(as.character(merged_data[[col_index]])), digits = 3)
}
```

```{r}
merged_data$SEX <- as.numeric(as.character(merged_data$SEX))
# or
# merged_data$column_name <- as.integer(as.character(merged_data$column_name))
print(merged_data$SEX)
merged_data
```

```{r}
merged_data[, 25:26] <- lapply(merged_data[, 25:26], as.integer)
merged_data
str(merged_data)
```

```{r}
names(merged_data) <- gsub("-", "_", names(merged_data))
merged_data
```




Central_venous_LSECs !
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Central_venous_LSECs <- ggscatter(data = merged_data, x = "mid.age", y = "Central_venous_LSECs", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
           main = "Cell type proportion according to age",xlab = "age", ylab = "Central_venous_LSECs
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Central_venous_LSECs.png", plot = p_Central_venous_LSECs)
```
```{r}
correlation_result <- cor.test(merged_data$Central_venous_LSECs, merged_data$mid.age, method = "spearman")

p_value_Central_venous_LSECs <- correlation_result$p.value

print(p_value_Central_venous_LSECs)
```

Cholangiocytes
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Cholangiocytes <- ggscatter(data = merged_data, x = "mid.age", y = "Cholangiocytes", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Cholangiocytes
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Cholangiocytes.png", plot = p_Cholangiocytes)
```
```{r}
correlation_result <- cor.test(merged_data$Cholangiocytes, merged_data$mid.age, method = "spearman")

p_value_Cholangiocytes <- correlation_result$p.value

print(p_value_Cholangiocytes)
```

Non_inflammatory_Macrophage !!
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Non_inflammatory_Macrophage <- ggscatter(data = merged_data, x = "mid.age", y = "Non_inflammatory_Macrophage", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Non_inflammatory_Macrophage
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Non_inflammatory_Macrophage.png", plot = p_Non_inflammatory_Macrophage)
```
```{r}
correlation_result <- cor.test(merged_data$Non_inflammatory_Macrophage, merged_data$mid.age, method = "spearman")

p_value_Non_inflammatory_Macrophage <- correlation_result$p.value

print(p_value_Non_inflammatory_Macrophage)
```

alpha_beta_T_Cells
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_alpha_beta_T_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "alpha_beta_T_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "alpha_beta_T_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_alpha_beta_T_Cells.png", plot = p_alpha_beta_T_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$alpha_beta_T_Cells, merged_data$mid.age, method = "spearman")

p_value_alpha_beta_T_Cells <- correlation_result$p.value

print(p_value_alpha_beta_T_Cells)
```

Inflammatory_Macrophage
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Inflammatory_Macrophage <- ggscatter(data = merged_data, x = "mid.age", y = "Inflammatory_Macrophage", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Inflammatory_Macrophage
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Inflammatory_Macrophage.png", plot = p_Inflammatory_Macrophage)
```
```{r}
correlation_result <- cor.test(merged_data$Inflammatory_Macrophage, merged_data$mid.age, method = "spearman")

p_value_Inflammatory_Macrophage <- correlation_result$p.value

print(p_value_Inflammatory_Macrophage)
```

NK_like_Cells !
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_NK_like_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "NK_like_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "NK_like_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_NK_like_Cells.png", plot = p_NK_like_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$NK_like_Cells, merged_data$mid.age, method = "spearman")

p_value_NK_like_Cells <- correlation_result$p.value

print(p_value_NK_like_Cells)
```

gamma_delta_T_Cells_1
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_gamma_delta_T_Cells_1 <- ggscatter(data = merged_data, x = "mid.age", y = "gamma_delta_T_Cells_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "gamma_delta_T_Cells_1
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_gamma_delta_T_Cells_1.png", plot = p_gamma_delta_T_Cells_1)
```
```{r}
correlation_result <- cor.test(merged_data$gamma_delta_T_Cells_1, merged_data$mid.age, method = "spearman")

p_value_gamma_delta_T_Cells_1 <- correlation_result$p.value

print(p_value_gamma_delta_T_Cells_1)
```

Hepatocyte_5
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_5 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_5", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_5
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_5.png", plot = p_Hepatocyte_5)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_5, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_5 <- correlation_result$p.value

print(p_value_Hepatocyte_5)
```

Portal_endothelial_Cells
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Portal_endothelial_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "Portal_endothelial_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Portal_endothelial_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Portal_endothelial_Cells.png", plot = p_Portal_endothelial_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$Portal_endothelial_Cells, merged_data$mid.age, method = "spearman")

p_value_Portal_endothelial_Cells <- correlation_result$p.value

print(p_value_Portal_endothelial_Cells)
```

gamma_delta_T_Cells_2
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_gamma_delta_T_Cells_2 <- ggscatter(data = merged_data, x = "mid.age", y = "gamma_delta_T_Cells_2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "gamma_delta_T_Cells_2
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_gamma_delta_T_Cells_2.png", plot = p_gamma_delta_T_Cells_2)
```
```{r}
correlation_result <- cor.test(merged_data$gamma_delta_T_Cells_2, merged_data$mid.age, method = "spearman")

p_value_gamma_delta_T_Cells_2 <- correlation_result$p.value

print(p_value_gamma_delta_T_Cells_2)
```

Periportal_LSECs
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Periportal_LSECs <- ggscatter(data = merged_data, x = "mid.age", y = "Periportal_LSECs", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Periportal_LSECs
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Periportal_LSECs.png", plot = p_Periportal_LSECs)
```
```{r}
correlation_result <- cor.test(merged_data$Periportal_LSECs, merged_data$mid.age, method = "spearman")

p_value_Periportal_LSECs <- correlation_result$p.value

print(p_value_Periportal_LSECs)
```

Hepatocyte_6
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_6 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_6", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_6
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_6.png", plot = p_Hepatocyte_6)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_6, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_6 <- correlation_result$p.value

print(p_value_Hepatocyte_6)
```

Mature_B_Cells
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Mature_B_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "Mature_B_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Mature_B_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Mature_B_Cells.png", plot = p_Mature_B_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$Mature_B_Cells, merged_data$mid.age, method = "spearman")

p_value_Mature_B_Cells <- correlation_result$p.value

print(p_value_Mature_B_Cells)
```

Hepatic_Stellate_Cells
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatic_Stellate_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatic_Stellate_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatic_Stellate_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatic_Stellate_Cells.png", plot = p_Hepatic_Stellate_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatic_Stellate_Cells, merged_data$mid.age, method = "spearman")

p_value_Hepatic_Stellate_Cells <- correlation_result$p.value

print(p_value_Hepatic_Stellate_Cells)
```

Plasma_Cells
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Plasma_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "Plasma_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Plasma_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Plasma_Cells.png", plot = p_Plasma_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$Plasma_Cells, merged_data$mid.age, method = "spearman")

p_value_Plasma_Cells <- correlation_result$p.value

print(p_value_Plasma_Cells)
```

Erythroid_Cells !
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Erythroid_Cells <- ggscatter(data = merged_data, x = "mid.age", y = "Erythroid_Cells", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Erythroid_Cells
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Erythroid_Cells.png", plot = p_Erythroid_Cells)
```
```{r}
correlation_result <- cor.test(merged_data$Erythroid_Cells, merged_data$mid.age, method = "spearman")

p_value_Erythroid_Cells <- correlation_result$p.value

print(p_value_Erythroid_Cells)
```

Hepatocyte_2
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_2 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_2
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_2.png", plot = p_Hepatocyte_2)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_2, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_2 <- correlation_result$p.value

print(p_value_Hepatocyte_2)
```

Hepatocyte_3 !!!!!!!!!!!!!!!!!!!!!!!
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_3 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_3", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_3
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_3.png", plot = p_Hepatocyte_3)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_3, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_3 <- correlation_result$p.value

print(p_value_Hepatocyte_3)
```

Hepatocyte_1
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_1 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_1
")
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_1.png", plot = p_Hepatocyte_1)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_1, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_1 <- correlation_result$p.value

print(p_value_Hepatocyte_1)
```

Hepatocyte_4
```{r}
# Load the necessary library
library(ggpubr)

# Create the scatter plot
p_Hepatocyte_4 <- ggscatter(data = merged_data, x = "mid.age", y = "Hepatocyte_4", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          main = "Cell type proportion according to age", xlab = "age", ylab = "Hepatocyte_4"
)
ggsave("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Hepatocyte_4.png", plot = p_Hepatocyte_4)
```
```{r}
correlation_result <- cor.test(merged_data$Hepatocyte_4, merged_data$mid.age, method = "spearman")

p_value_Hepatocyte_4 <- correlation_result$p.value

print(p_value_Hepatocyte_4)
```





```{r}
pvalues <- c(p_value_Hepatocyte_4, p_value_Hepatocyte_1, p_value_Hepatocyte_3, p_value_Hepatocyte_2, p_value_Erythroid_Cells, p_value_Plasma_Cells, p_value_Hepatic_Stellate_Cells, p_value_Mature_B_Cells, p_value_Hepatocyte_6, p_value_Periportal_LSECs, p_value_gamma_delta_T_Cells_2, p_value_Portal_endothelial_Cells, p_value_Hepatocyte_5, p_value_NK_like_Cells, p_value_Inflammatory_Macrophage, p_value_Non_inflammatory_Macrophage, p_value_Cholangiocytes, p_value_Central_venous_LSECs)

p.adjust(pvalues,method="bonferroni")
```
no significant correlation for all except => Hepatocyte 3 

```{r}
pvalues <- c(p_value_Hepatocyte_4, p_value_Hepatocyte_1, p_value_Hepatocyte_3, p_value_Hepatocyte_2, p_value_Erythroid_Cells, p_value_Plasma_Cells, p_value_Hepatic_Stellate_Cells, p_value_Mature_B_Cells, p_value_Hepatocyte_6, p_value_Periportal_LSECs, p_value_gamma_delta_T_Cells_2, p_value_Portal_endothelial_Cells, p_value_Hepatocyte_5, p_value_NK_like_Cells, p_value_Inflammatory_Macrophage, p_value_Non_inflammatory_Macrophage, p_value_Cholangiocytes, p_value_Central_venous_LSECs)

p.adjust(pvalues,method="BH")
```
no significant correlation for all except => Hepatocyte 3 

p_value_Hepatocyte_3

0.05

```{r}
data_long <- merged_data %>%
  pivot_longer(cols = c("Central_venous_LSECs", "Cholangiocytes", "Inflammatory_Macrophage", "Inflammatory_Macrophage", "NK_like_Cells", "gamma_delta_T_Cells_2", "Periportal_LSECs", "Hepatocyte_6", "Mature_B_Cells", "Hepatic_Stellate_Cells", "Plasma_Cells", "Erythroid_Cells", "Hepatocyte_2", "Hepatocyte_3", "Hepatocyte_1", "Hepatocyte_4", "Hepatocyte_5", "Portal_endothelial_Cells"), names_to = "Cell_Type", values_to = "Fraction")
##removing O
```

```{r}
data_long
```


```{r}
library(viridis)
library(ggplot2)
library(dplyr)

# Generate a sequence of colors using the viridis palette
colors <- viridis(20)

# Create the plot
p2 <- data_long %>%
  group_by(AGE, Cell_Type) %>%
  summarise(mf = mean(Fraction)) %>%
  ungroup() %>%
  ggplot(aes(y = AGE, x = mf, fill = Cell_Type)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d() +
  labs(y = "Mid Age", x = "Fraction of Cell Types") +
  theme_minimal() +
  coord_flip() +
  theme(
    legend.key.width = unit(0.5, "cm"),  # Decrease the width of legend key
    legend.key.height = unit(0.5, "cm")  # Decrease the height of legend key
  )

# Display the plot
print(p2)

# Save the plot
png("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p_Liver_Cell_Comp.png", 
    width = 6, height = 4, units = "in", res = 800)
print(p2)  # Print the plot again inside the PNG device
dev.off()
```

```{r}
p2_age <- barplot(table(merged_data$AGE), 
        main = "Age of our samples",
        xlab = "Age",
        ylab = "Number of samples")

p2_age <- recordPlot()
png("C:\\Users\\lorca\\Documents\\Project\\2 Liver\\Liver_\\Images\\p2_Liver_Age_Nb.png", width = 6, height = 4, units = "in", res = 800)
replayPlot(p2_age)
dev.off()
```
```{r}
# Calculate the total number of samples
total_samples <- sum(table(merged_data$AGE))

# Print the total number of samples
cat("Total samples:", total_samples, "\n")

```

